Cosmological constraints from the redshift dependence of the galaxy angular 2-point correlation function

### 2016-08-30 draft/draft0.tex
updates

In case we adopted a wrong set of cosmological parameters in Equation (\ref{eq:distance},\ref{eq:HDA}),
the inferred $\Delta r_{\parallel}$ and $\Delta r_{\bot}$ are wrong,
resulting in distorted shape (AP effect) and wrongly estimated volume (volume effect).
These effects have been discussed in \cite{Li2014,Li2015,Li2016}.
This paper we focus on the misestimation of $\Delta r_{\bot}$,%scaling of angular size,
which can be described by the following quantities
\begin{equation}\label{eq:DA}
 %{\rm Degree\ of\ volume\ magnification \equiv}
 %{\rm rat}_{\rm volume\ mag}\equiv
 \frac{\Delta r_{\bot, \rm wrong}}{\Delta r_{\bot, \rm true}}
 = \frac{D_{A, \rm wrong}}{D_{A, \rm true}},
\end{equation}
where ``true'' and ``wrong'' denote the values of $D_A$ in the true cosmology and wrongly assumed cosmology.

@@

\begin{figure*}
   \centering{
%   \includegraphics[width=18cm]{fig9_0.eps}
%   \includegraphics[width=18cm]{fig9_1.eps}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
    \includegraphics[width=18cm]{fig3.eps}
   }
   \caption{\label{fig_diffz}
  2pCF at different redshfits.
   }
\end{figure*}

@@

>>>>

In case we adopted a wrong set of cosmological parameters in Equation (\ref{eq:distance},\ref{eq:HDA}),
the inferred $\Delta r_{\parallel}$ and $\Delta r_{\bot}$ are wrong,
resulting in distorted shape (AP effect) and wrongly estimated volume (volume effect).
These effects have been discussed in \cite{Li2014,Li2015,Li2016}.
This paper we focus on the misestimation of $\Delta r_{\bot}$,%scaling of angular size,
which can be described by the following quantities
\begin{equation}\label{eq:DA}
 %{\rm Degree\ of\ volume\ magnification \equiv}
 %{\rm rat}_{\rm volume\ mag}\equiv
 \alpha_{\bot} \equiv \frac{\Delta r_{\bot, \rm wrong}}{\Delta r_{\bot, \rm true}}
 = \frac{D_{A, \rm wrong}}{D_{A, \rm true}},
\end{equation}
where ``true'' and ``wrong'' denote the values of $D_A$ in the true cosmology and wrongly assumed cosmology.

@@

\begin{figure*}
   \centering{
%   \includegraphics[width=18cm]{fig9_0.eps}
%   \includegraphics[width=18cm]{fig9_1.eps}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
    \includegraphics[width=18cm]{fig3.eps}
    \includegraphics[width=18cm]{fig3_b.eps}
   }
   \caption{\label{fig_diffz}
  2pCF at different redshfits.
   }
\end{figure*}

@@

When a wrong set of cosmological parameters is adopted,
the galaxy distribution is artificially scaled.
This scaling is expected to change the shape of the 2pCF,
following the relationship,
\begin{equation}
 \hat \xi_{\rm wrong}(r) = \hat\xi_{\rm true}(\alpha_{\bot} r),
\end{equation}
a simple consequence of the fact that clustering patterns at distance $r$ now appears on a the scale $\alpha_{\bot} r$.
The redshift evolution of $\alpha_{\bot}$ leads to redshfit evolution of shape.

\begin{figure*}
   \centering{
%   \includegraphics[width=18cm]{fig9_0.eps}
%   \includegraphics[width=18cm]{fig9_1.eps}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}

   }
   \caption{\label{fig_cosmo}
   2pCF in cosmologies.
   }
\end{figure*}

Lower panels of Figure \ref{fig_diffz} shows the $r\xi$ in five 
snapshots, in case that the cosmology $\Omega_m=0.05,\ w=-1.5$ 
is adopted to construct the galaxy distribution (the right panels of Figure \ref{fig_scatter}).
The middle panel displays the clear redshift evolution of shape of $r\xi$.
E.g, from $z=0$ to $z=2$,
the peak location is shifted from $r=9h^{-1} \rm Mpc$ to $r\sim15 h^{-1}\rm Mpc$ at $z=2$
since the angular separation is upscaled by $71.7\%$.

The right panel shows that, 
at higher redshift, 
there is a 20-40\% change in the value of $\hat {r\xi}$.

The amplitude of $r\xi$ is amplified due to the stretch of scale.
As shown in the left panel, the amplitude monotonically increases as a function of redshift.
But this phenomenon can also appear in case of gravitational growth of structure or increasing of bias,
so we will not make use of it to do cosmological constraint.
We utilize the redshift evolution of the 2pCF shape as a signal suggesting that the assumed cosmological parameters are wrong.

In Figure \ref{fig_cosmo} we further plot the redshift evolution of 2pCF in the four wrong cosmologies of Figure \ref{fig_xyquan}.
In all cases, the scaling leads to evident redshift evolution of the shape of $r\xi$.
When the cosmologies $\Omega_m=0.4,w=-1$ and $\Omega_m=0.26,w=-0.5$ are adopted,
the compression of structure makes the clustering patterns appears on smaller scales.
This leads to ``steeper'' slope of $r\xi$, 
and the higher the redshift, the steeper the slope.
To the opposite, when adopting the cosmologies $\Omega_m=0.15,w=-1$ and $\Omega_m=0.26,w=-1.5$,
the stretch of size makes the slope shallower at higher redshfits.

\subsection{Systematic effects}

\subsection{Likelihood Analysis}

One can build up a likelihood function to 
describe how significant is the redshift evolution of the 2pCF shape
so that to determine whether the adopted cosmological parameters are correct.
\begin{equation}\label{eq:chisq1}
\chi^2\equiv \sum_{i=2}^{6} \sum_{j_1=1}^{n_{\mu}} \sum_{j_2=1}^{n_{\mu}} {\bf p}(z_i,\mu_{j_1}) ({\bf Cov}_{i}^{-1})_{j_1,j_2}  {\bf p}(z_i,\mu_{j_2}),
\end{equation}
where ${\bf p}(z_i,\mu_{j})$ is the redshift evolution of clustering, 
$\hat \xi_{\Delta s}$, with systematic effects subtracted
\begin{eqnarray}\label{eq:bfp}
 {\bf p}(z_i,\mu_{j}) \equiv&\ \delta \hat{r\xi}(z_i,z_1,\mu_j) - \delta \hat{r\xi}_{\rm sys}(z_i,z_1,\mu_j)
\end{eqnarray}
${\bf Cov}_i$ is the covariance matrix estimated from the 72 sets of PSB mock galaxies identified from HR3 N-body simulation.
